R Notebook

### 2023-11-01 Tensor MSSA.rmd
Add comments

# rank of the time series
r <- 1
s <- map(1:series.number, function(x) runif(1, 1, 4) * exp(1:N * runif(1, 0.001, 0.07)))
s.hankel <- lapply(s, hankel, L)
mat <- reduce(s.hankel, cbind)
u.svd <- svd(mat)
# signal subspace
true.subspace <- u.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
```

```{r}
LPA.mat <- numeric(iterations)
LPA.tens <- numeric(iterations)
mse.mat <- matrix(0, ncol = iterations, nrow = series.number)
mse.tens <- matrix(0, ncol = iterations, nrow = series.number)
pb <- txtProgressBar(max = iterations, style = 3)
for (i in 1:iterations) {
  # noised case
  s.n <- lapply(s, function(x) x + rnorm(N, sd = sigma))
  # noiseless case
  # s.n <- s
  s.n.hankel <- lapply(s.n, hankel, L)
  mat.n <- reduce(s.n.hankel, cbind)
  u.n.svd <- svd(mat.n)
  est.subspace <- u.n.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
  mat.rec <- reconstruct(ssa(s.n, L = L, kind = "mssa"), groups = list(1:r))[[1]]

>>>>

# rank of the time series
r <- 1
# generating series with ranodm parameters
# s <- map(1:series.number, function(x) runif(1, 1, 4) * exp(1:N * runif(1, 0.001, 0.07)))
# generating series by hand
s <- map(1:series.number, function(x) exp(1:N * x / 1000))
s.hankel <- lapply(s, hankel, L)
mat <- reduce(s.hankel, cbind)
u.svd <- svd(mat)
# signal subspace
true.subspace <- u.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
```

```{r}
LPA.mat <- numeric(iterations)
LPA.tens <- numeric(iterations)
mse.mat <- matrix(0, ncol = iterations, nrow = series.number)
mse.tens <- matrix(0, ncol = iterations, nrow = series.number)
pb <- txtProgressBar(max = iterations, style = 3)
for (i in 1:iterations) {
  # noised case
  # s.n <- lapply(s, function(x) x + rnorm(N, sd = sigma))
  # noiseless case
  s.n <- s
  s.n.hankel <- lapply(s.n, hankel, L)
  mat.n <- reduce(s.n.hankel, cbind)
  u.n.svd <- svd(mat.n)
  est.subspace <- u.n.svd$u[, 1:min(r, N - L + 1), drop = FALSE]
  mat.rec <- reconstruct(ssa(s.n, L = L, kind = "mssa"), groups = list(1:r))[[1]]
